---
title: "Assignment 1 – Data Analysis using R Programming"
output: pdf_document
date: "2024-02-08"
---
----
Group 3
Yuen Ting Kung
Ceci Lau
Christopher Sta. Romana
Giwoon Yang
Alex Sydfrey Ygusguiza
Man Chun, Yuen
Lawrence Wu
----

```{r}
library(ggplot2)
library(readxl)
covid_19_data <- read_excel("covid_19_data.xlsx")
library(tidyverse)
```
## •Print the structure of your dataset
```{r}
str(covid_19_data)
```
## •List the variables in your dataset
```{r}
names(covid_19_data)
```
## •Print the top 15 rows of your dataset
```{r}
head(covid_19_data, n = 15)
```
## •Write a user defined function using any of the variables from the data set
```{r}
# Function that calculates the average recovered covid cases
avg_recovered <- function(data) {
  return(mean(covid_19_data$Recovered))
}

# Example:
avg_recovered(covid_19_data)
```
## •Use data manipulation techniques and filter rows based on any logical criteria that exist in your dataset
```{r}
country_reg = as.data.frame(covid_19_data %>% filter(covid_19_data$`Country/Region` == "Taiwan"))
head(country_reg)
```
## •Identify the dependent & independent variables and use reshaping techniques and create a new data frame by joining those variables from your dataset
```{r}
cov19_new = as.data.frame((covid_19_data %>% select(3,6:8)))
head(cov19_new)
```
## • Remove missing values in your dataset
```{r}
na.omit(covid_19_data)
```
## •Identify and remove duplicated data in your dataset
```{r}
covid_19_data_test <- read_excel("covid_19_data_test.xlsx")

# Identifty duplicated data
duplicated(covid_19_data_test)

# Remove duplicated data
cov19_unique = unique(covid_19_data_test)

# Run duplicated operation again, expected output: all entry is FALSE 
duplicated(cov19_unique)
```
## •Reorder multiple rows in descending order
```{r}
covid_19_data %>% arrange(desc(SNo))
```
## •Rename some of the column names in your dataset
```{r}
covid_19_data %>% rename(Observation_Date = ObservationDate, Province_State =`Province/State`)
```
## •Add new variables in your data frame by using a mathematical function (for e.g. – multiply an existing column by 2 and add it as a new variable to your data frame)
```{r}
covid_19_data = as.data.frame(covid_19_data %>% mutate(New.Status = covid_19_data$Confirmed - 
                                                         covid_19_data$Recovered))
head(covid_19_data)
```
## •Create a training set using random number generator engine
```{r}
cov19_training = cbind(covid_19_data$`Province/State`, covid_19_data$`Country/Region`, 
                       covid_19_data$Confirmed, covid_19_data$Recovered)
cov19_training = as.data.frame(cov19_training)
set.seed(1234)

cov19_training = as.data.frame(cov19_training %>% sample_frac(0.8, replace = FALSE))
head(cov19_training)

# Run generator again to show difference
cov19_training = as.data.frame(cov19_training %>% sample_frac(0.8, replace = FALSE))
head(cov19_training)
```
## •Print the summary statistics of your dataset
```{r}
summary(covid_19_data)
```
## •Use any of the numerical variables from the dataset and perform the following statistical functions
```{r}
# Mean of confirmed cases
conf_mean <- c(covid_19_data$Confirmed) 
result.mean <- mean(conf_mean)
print(result.mean)

# Median of deaths
death_median <- c(covid_19_data$Deaths) 
result.median <- mean(death_median)
print(result.median)

# Mode of range of Country/Region
reg_mode <- c(covid_19_data$`Country/Region`)
result.mode <- mode(reg_mode)
print(result.mode)

# Range of recovered cases
print(range(covid_19_data$Recovered))
```
## •Plot a scatter plot for any 2 variables in your dataset
```{r}
# Scatter plot of covid deaths against confirmed cases
ggplot(covid_19_data, aes(x = Deaths, y = Confirmed)) + geom_point(size = 1.2, color = "red2",
                                                                   shape = 21)
```


## •Plot a bar plot for any 2 variables in your dataset


```{r}
# Bar Plot of covid deaths per country
ggplot(covid_19_data, aes(x = `Country/Region`, fill = Deaths))+geom_bar(fill = "chocolate1")
```


## •Find the correlation between any 2 variables by applying least square linear regression model
```{r}
# Correlation of confirmed covid cases againts recovered cases
cov19_corr = cor(covid_19_data$Confirmed, covid_19_data$Recovered, method = "pearson")
cov19_corr
```

^[The .RMD file, PDF report, and the dataset can be found on https://github.com/alexsydfrey/Data-Analysis-using-R]